### 2025-03-07 manuscript/manuscript.qmd
Responses to CA and one in-text citation fixed

<!-- Note. there is no clear conversion from Average precision to MCC, although we could estimate this from our data using regression? or to calculate both metrics from the confusion matrix. CA: this sounds like an interesting and achievable idea. The confusion matrices are encoded and then summarized with the caret and yardstick packages, and we can potentially extract many other useful measures from them with yardstick::summary(), demonstrated here: https://yardstick.tidymodels.org/reference/summary.conf_mat.html -->

@@

CA: This is a great idea, and reminds me we also have the Panda categories, which we have encoded, but haven't touched. We could explore whether we can find additional patterns about feature categories, and possibly libraries by extending out our new heat map visualization approach. -->
```

@@

```{=html}
<!-- Question to @Cameron: Could you add some of the studies included in the meta-analysis in the references to those studies that do not share datasets to make this more relevant. I just copied two references that I know are examples of datasets that require extra steps, but we have studies where we just don't even know whether the data is available, right?

CA: I've added some studies now, though these were excluded from the final meta-analysis. I also have a few examples of those which were included in the final results based on scrolling through the articles. Many are psychology papers, where it seems less common to share data publicly, but those also tend to have more case-specific goals rather than comparing results to existing benchmarks, so I didn't cite them. @hizlisoy2021mu proposes a new turkish music database, but I wasn't able to find the data from the article, so I added that. @zhang2017fe uses a dataset but doesn't seem to provide information on how to access it. -->
```

>>>>

<!-- Note. there is no clear conversion from Average precision to MCC, although we could estimate this from our data using regression? or to calculate both metrics from the confusion matrix. CA: this sounds like an interesting and achievable idea. The confusion matrices are encoded and then summarized with the caret and yardstick packages, and we can potentially extract many other useful measures from them with yardstick::summary(), demonstrated here: https://yardstick.tidymodels.org/reference/summary.conf_mat.html.

TE: Interesting, it is a potential weakness and it would make our promotion of MCC more valuable when we could demonstrate how these two are linked, but perhaps to limit the workload, we could try identify a small subset to which to apply to this idea. -->

@@

CA: This is a great idea, and reminds me we also have the Panda categories, which we have encoded, but haven't touched. We could explore whether we can find additional patterns about feature categories, and possibly libraries by extending out our new heat map visualization approach.

TE: Or if we submit the meta-analysis soon and create a more pragmatic breakdown of what is the state of the art technologies in MER, this could be sufficient for a brief article separately. The selling point would not be the prediction rate, but quality control issues and the techniques/tools/crossvals/datasets chosen so far.  -->
```

@@

```{=html}
<!-- Question to Cameron: Could you add some of the studies included in the meta-analysis in the references to those studies that do not share datasets to make this more relevant. I just copied two references that I know are examples of datasets that require extra steps, but we have studies where we just don't even know whether the data is available, right?

CA: I've added some studies now, though these were excluded from the final meta-analysis. I also have a few examples of those which were included in the final results based on scrolling through the articles. Many are psychology papers, where it seems less common to share data publicly, but those also tend to have more case-specific goals rather than comparing results to existing benchmarks, so I didn't cite them. @hizlisoy2021mu proposes a new turkish music database, but I wasn't able to find the data from the article, so I added that. @zhang2017fe uses a dataset but doesn't seem to provide information on how to access it.
TE: great, well done, job done. -->
```
